### 2021-04-19 paper/ase21/abstract.tex
[ASE21] Updated abstract

  To alleviate the problem, we propose $\tool$, a JavaScript Specification Type
  Analyzer using Refinement.  It is the first tool that performs \textit{type
  analysis} on JavaScript specifications and detects specification bugs using a
  \textit{bug detector}.  For a given specification, $\tool$ first compiles each
  abstract algorithm written in a structured natural language to a corresponding
  function in $\ires$, an untyped intermediate representation for ECMAScript.
  Then, it performs type analysis for compiled functions with specification
  types defined in ECMAScript.  Based on the result of type analysis, $\tool$
  detects specification bugs using a bug detector consisting of four checkers.
  Moreover, to increase precision of type analysis, we present
  \textit{condition-based refinement} for type analysis, which prunes out
  infeasible abstract states using conditions of assertions and branches.  We
  evaluated $\tool$ with all 864 versions in the official ECMAScript repository
  for the recent three years from 2018 to 2021.  Our tool took \inred{230}
  seconds on average to perform type analysis for each version, and detected
  \inred{200} type-related specification bugs with \inred{50.3}\% precision;
  \inred{91} out of \inred{200} bugs are true bugs.  Among them, \inred{14} bugs
  are newly detected by $\tool$ and the committee confirmed all of them.
\end{abstract}

>>>>

  To alleviate the problem, we propose $\tool$, a JavaScript Specification Type
  Analyzer using Refinement.  It is the first tool that performs \textit{type
  analysis} on JavaScript specifications and detects specification bugs using a
  \textit{bug detector}.  For a given specification, $\tool$ first compiles each
  abstract algorithm written in a structured natural language to a corresponding
  function in $\ires$, an untyped intermediate representation for ECMAScript.
  Then, it performs type analysis for compiled functions with specification
  types defined in ECMAScript.  Based on the result of type analysis, $\tool$
  detects specification bugs using a bug detector consisting of four checkers.
  Moreover, to increase precision of type analysis, we present
  \textit{condition-based refinement} for type analysis, which prunes out
  infeasible abstract states using conditions of assertions and branches.  We
  evaluated $\tool$ with all 864 versions in the official ECMAScript repository
  for the recent three years from 2018 to 2021.  Our tool took \inred{136.1}
  seconds on average to perform type analysis for each version, and detected
  \inred{177} type-related specification bugs with \inred{52.0}\% precision;
  \inred{92} bugs out of \inred{177} bugs are true bugs.  Among them, \inred{14}
  bugs are newly detected by $\tool$ and the committee confirmed all of them.
\end{abstract}
